Plot Scenarios

### 2025-04-30 PlotScenarios.Rmd
added Cheng's code from 4/29 but not 4/30, email cut off

Catch
```

>>>>

Catch
```
Add in Cheng's new plotting functions

```{r}
source(here::here("helper.R"))
```

Cheng's example modified from `MSE_plot_code.R`

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(fmsb)
library(ggpubr)
library(gridExtra)
library(rmarkdown)

main.dir = getwd()

sub.dir <- 'Report'
output_dir <- file.path(main.dir,sub.dir)

if(!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
}

model_nums <- c(1,4)
nsim <- 50 # number of simulations/seed

mods <- vector("list", nsim)

for (r in 1:nsim) {
  mods[[r]] <- vector("list", length(model_nums))
  names(mods[[r]]) <- paste0("Mod", model_nums)

  for (m in model_nums) {
    file_path <- file.path("Results/", sprintf("Mod%d_%03d.RDS", m, r))
    mods[[r]][[paste0("Mod", m)]] <- readRDS(file_path)
  }
}

if (!is.list(mods[[1]][[1]][[1]])) is.nsim = FALSE else is.nsim = TRUE

cat("\nPloting SSB Time Series...\n")

plot_ssb_time_series(mods, is.nsim, main.dir, sub.dir, var = "SSB",
                     width = 10, height = 7, dpi = 300,
                     new_model_names = NULL) # you can change the Model name here

cat("\nPloting Fbar Time Series...\n")

plot_fbar_time_series(mods, is.nsim, main.dir, sub.dir, var = "Fbar",
                      width = 10, height = 7, dpi = 300,
                      new_model_names = NULL)

cat("\nPloting Catch Time Series...\n")

plot_catch_time_series(mods, is.nsim, main.dir, sub.dir, var = "Catch",
                       width = 10, height = 7, dpi = 300,
                       new_model_names = NULL)

cat("\nPloting SSB Performance Over Last n Years...\n")

# Long-term performance #
# Default = 5 years #

plot_ssb_performance(mods, is.nsim, main.dir, sub.dir, var = "SSB",
                     width = 10, height = 7, dpi = 300,
                     new_model_names = NULL,
                     use.n.years = NULL)

cat("\nPloting Fbar Performance Over Last n Years...\n")

plot_fbar_performance(mods, is.nsim, main.dir, sub.dir, var = "Fbar",
                      width = 10, height = 7, dpi = 300,
                      new_model_names = NULL,
                      use.n.years = NULL)

cat("\nPloting Catch Performance Over Last n Years...\n")

plot_catch_performance(mods, is.nsim, main.dir, sub.dir, var = "Catch",
                       width = 10, height = 7, dpi = 300,
                       new_model_names = NULL,
                       use.n.years = NULL)

cat("\nPloting SSB Performance Over First n Years...\n")

# -----------------------
# Short-term performance
# -----------------------
# summarize first 10 years in the feedback period
start.years = 31 
use.n.years = 10

plot_ssb_performance2(mods, is.nsim, main.dir, sub.dir, var = "SSB",
                      width = 10, height = 7, dpi = 300,
                      new_model_names = NULL,
                      use.n.years = use.n.years,
                      start.years = start.years)

cat("\nPloting Fbar Performance Over First n Years...\n")

plot_fbar_performance2(mods, is.nsim, main.dir, sub.dir, var = "Fbar",
                       width = 10, height = 7, dpi = 300,
                       new_model_names = NULL,
                       use.n.years = use.n.years,
                       start.years = start.years)

cat("\nPloting Catch Performance Over First n Years...\n")

plot_catch_performance2(mods, is.nsim, main.dir, sub.dir, var = "Catch",
                        width = 10, height = 7, dpi = 300,
                        new_model_names = NULL,
                        use.n.years = use.n.years,
                        start.years = start.years)

cat("\nPloting SSB Status and Probability of Overfished Over Last n Years...\n")

plot_ssb_status(mods, is.nsim, main.dir, sub.dir, var = "SSB_status",
                width = 10, height = 7, dpi = 300,
                new_model_names = NULL,
                use.n.years = NULL)

cat("\nPloting Fbar Status and Probability of Overfishing Over Last n Years...\n")

plot_fbar_status(mods, is.nsim, main.dir, sub.dir, var = "Fbar_status",
                 width = 10, height = 7, dpi = 300,
                 new_model_names = NULL,
                 use.n.years = NULL)

cat("\nPloting SSB Status and Probability of Overfished Over First n Years...\n")

# -----------------------
# Short-term performance
# -----------------------
# summarize first 10 years in the feedback period
start.years = 31 
use.n.years = 10

plot_ssb_status2(mods, is.nsim, main.dir, sub.dir, var = "SSB_status",
                 width = 10, height = 7, dpi = 300,
                 new_model_names = NULL,
                 use.n.years = use.n.years,
                 start.years = start.years)

cat("\nPloting Fbar Status and Probability of Overfishing Over First n Years...\n")

plot_fbar_status2(mods, is.nsim, main.dir, sub.dir, var = "Fbar_status",
                  width = 10, height = 7, dpi = 300,
                  new_model_names = NULL,
                  use.n.years = use.n.years,
                  start.years = start.years)
